---
title: "Homework 5"
author: "Julia Thompson"
date: "11/5/2019"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(rvest)

knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	fig.width = 8, 
  fig.height = 6,
  out.width = "90%"
)
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
theme_set(theme_minimal() + theme(legend.position = "bottom"))
```

## Problem 1

```{r}
set.seed(10)

iris_with_missing = iris %>% 
  map_df(~replace(.x, sample(1:150, 20), NA)) %>%
  mutate(Species = as.character(Species))
```

There are two cases to address:

For numeric variables, you should fill in missing values with the mean of non-missing values
For character variables, you should fill in missing values with "virginica"
Write a function that takes a vector as an argument; replaces missing values using the rules defined above; and returns the resulting vector. 

```{r}
mean_sepal = mean(pull(iris_with_missing, Sepal.Length), na.rm=TRUE)

test_replace = tibble(replace_na(pull(iris_with_missing, Sepal.Length), mean_sepal))

rest2_replace = tibble(replace_na(pull(iris_with_missing, Species), "virginica"))
```

```{r}
# Want a function that takes in 1 vector and outputs another vector with missing values replaced

replace_missing_fn = function(vector) {
  
  if(length(vector) == 1){
    stop("Argument cannot be computed for length 1 vectors")
  }
  
  else if(is.numeric(vector)) {
    mean = mean(vector, na.rm=TRUE)
    tibble(
      replace_na(vector, mean)
    )
  }
  
  else if (!is.numeric(vector)) {
    tibble(
      replace_na(vector, "virginica")
    )
  }
}

# Test the function

replace_missing_fn(pull(iris_with_missing, Sepal.Length))

# replace_missing_fn(2)

replace_missing_fn(pull(iris_with_missing, Species))

```

Apply this function to the columns of iris_with_missing using a map statement.

```{r}
output = map(iris_with_missing, replace_missing_fn) %>% 
  bind_cols()
```

